The Exoplanet Orbit Database 2, 2014 updates

### 2014-03-17 draft/ms.tex
Refine Sec 2.2.

The rest of the selection criteria for the EOD remain unchanged. We
still require the planets to be smaller than 24 \mjup\ and to have
robust detections and well-determined orbits (though these are not
strictly quantitative; see Section~2 of \citealt{Wright2011}).

@@

{\bf MICROLENSING, IMAGING, TIMING and ASTROMETRY} are flags which
indicate that a planet detected via theses methods. For example,
MICROLENSING $=$ 1 means the planet is detected in a microlensing
event. However, we require the detection to be robust, as determined
by the QUAlity Control Board of the Exoplanet Database, QUACBED (see
Section~\ref{sec:kepler}.

@@

{\bf MASS} is the mass of the planet in the unit of Jupiter
mass. Previously, we only reported the minimum mass, ($m\sin{i}$,
MSINI) of the planets. We now report the mass as well when it is
available. For example, if a planet is discovered by microlensing, we
report the actual mass of the planet according to the literature. If a
planet has both radial velocity and transit measurements, we calculate
the mass from the minimum mass and the orbital inclination. MASS is
set to MSINI if the orbital inclination is not given and the MASSREF
is set to ``Set to MSINI; I unknown''.

For KOIs without MSINI measured, we calculate their mass using the
mass-radius relation from the literatures. For KOIs with $R<4\rearth$,
we use \cite{Weiss2014} , with $4\rearth<R<6\rearth$, we use
\cite{Lissauer2011}, and for KOIs with $6\rearth<R<11.7\rearth$ we use
\cite{Mordasini2012}.

{\bf SEP} is the projected separation on the sky between the host star
and the planet in the unit of AU. For directly imaged planets, the
literatures give the projected separation and we report this value.
If SEP is not directly measured but the semi-major (A) is available,
then SEP is set to A with the reference ``Set to A''. For the cases
where only the projected separation is given such as imaged planets,
then the semi-major axis is set to SEP.

{\bf I} is the orbital inclination. Previously, only transiting
systems have I measured but now, sometimes, non-transiting systems
have I's reported too. For example, one microlensing system has I
measured (OGLE-2006-BLG-109L; \citealt{Bennet2010}).

{\bf BIGOM} is the longitude of the ascending node ($\Omega$) in the
unit of degree and for now this is only measured for some of the
directly imaged planets, which are not in the EOD.

{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
the unit of degree. We report the projected spin-orbit misalignment of
transiting systems, which is measured by, e.g., the
Rossiter-McLaughlin effect \citep[e.g.,][]{Winn2005} or planet
transiting star spots \citep[e.g.,][]{Sanchis-Ojeda2012}. $\lambda$ is
introduced because the true spin-orbit angle ($\phi$), defined as the
angle between the stellar spin axis and the orbital axis, is normally
not directly measurable. We follow the definition of $\lambda$ in
\cite{Fabrycky2009} where the coordinates are defined as follows; the
$z$-axis points toward the observer, the $x$-axis points along the
intersection of the sky plane and the planet's orbital plane with the
ascending node of the planet having $x<0$, and the $y$-axis completes
a right handed-triad. $\lambda$ is measured clockwise on the sky from
the $y$-axis to the projected stellar rotational axis. $\lambda$ is
not a newly added field but we describe it here because $\lambda$'s
were not reported consistently since some literatures report $\beta =
-\lambda$ instead. We sorted these cases out and made sure that our
$\lambda$'s are following the definition of \cite{Fabrycky2009}.

>>>>

The rest of the selection criteria for the EOD remain unchanged. We
still require the planets to be smaller than 24 \mjup\ and to have
robust detections and well-determined orbits (though these are not
strictly quantitative; see Section~2 of \citealt{Wright2011}). When
new evidence comes to light and we are no longer confident about the
planet, we remove it from EOD, even if the evidence is not peer
reviewed.

@@

{\bf MICROLENSING, IMAGING, TIMING and ASTROMETRY} are flags which
indicate that a planet detected via theses methods. For example,
MICROLENSING $=$ 1 means the planet is detected in a microlensing
event. However, we require the detection to be robust, as determined
by the QUAlity Control Board of the Exoplanet Database, QUACBED (see
Section~\ref{sec:kepler}).

@@

{\bf MASS} is the mass of the planet in the unit of Jupiter
mass. Previously, we only reported the minimum mass, ($m\sin{i}$,
MSINI) of the planets. We now report the mass as well when it is
available. For example, if a planet is discovered by microlensing, we
report the actual mass of the planet according to the literature. If a
planet has both radial velocity and transit measurements, we calculate
the mass from the minimum mass $m\sin{i}$ and the orbital inclination
$i$. MASS is set to MSINI if the orbital inclination is not given and
the reference for MASS, MASSREF is set to ``Set to MSINI; I unknown''.

For KOIs without MSINI measured, we calculate their mass using the
mass-radius relation from the literatures. For KOIs with $R<4\rearth$,
we follow \cite{Weiss2014}; for $4\rearth<R<6\rearth$, we follow
\cite{Lissauer2011}; and for $6\rearth<R<11.7\rearth$ we follow
\cite{Mordasini2012}.

{\bf SEP} is the projected separation on the sky between the host star
and the planet in the unit of AU. For directly imaged planets, the
literatures usually report the projected separation and we report the
value accordingly.  If SEP is not directly measured but the semi-major
axis ($a$, A) is available, then SEP is set to A with its reference,
SEPREF, set to ``Set to A''. For the cases where only the projected
separation is given but A is not available (e.g., the directly imaged
planets), then A is set to SEP.

{\bf I} is the orbital inclination. Previously, only transiting
systems have I measured, but now some non-transiting systems
have I's reported too. For example, one microlensing system,
OGLE-2006-BLG-109L, has I measured \citep{Bennett2010}.

{\bf BIGOM} is the longitude of the ascending node ($\Omega$) in the
unit of degree. At the moment, this is only measured for some of the
directly imaged planets, which are not in the EOD.

{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
the plane of the sky in the unit of degree. At the moment, $\lambda$
values are only available for the transiting systems, which are
measured by either the Rossiter-McLaughlin effect
\citep[e.g.,][]{Winn2005} or planet transiting star spots
\citep[e.g.,][]{Sanchis-Ojeda2012}. $\lambda$ is introduced because
the true spin-orbit angle ($\phi$), defined as the angle between the
stellar spin axis and the orbital axis, is normally not directly
measurable. We follow the definition of $\lambda$ in
\cite{Fabrycky2009} where the coordinates are defined as follows: the
$z$-axis points toward the observer, the $x$-axis points along the
intersection of the sky plane and the planet's orbital plane with the
ascending node of the planet having $x<0$, and the $y$-axis completes
a right handed-triad. $\lambda$ is measured clockwise on the sky from
the $y$-axis to the projected stellar rotational axis. $\lambda$ is
not a newly added field but we describe it here because it was not
reported consistently since some literatures report the ``projected
spin-orbit misalignment" as $\beta = -\lambda$ instead. We have sorted
these cases out and made sure that our $\lambda$'s are following the
definition of \cite{Fabrycky2009}.
